Storing messages with multipartite neural cliques

### 2014-06-28 Articles/article.tex
Explication des indices.
amélioration gamma
Ajout formule en latex

@@

>>>>

	gc : good (à remplacer par right) neuron in correct cluster

	ge : good neuron in erroneous cluster

	abe : bad activated neuron in erroneous cluster

	be : others bad (à remplacer par wrong ou incorrect etc.) neurons in erroneous cluster

	bc : bad neuron in correct cluster

@@

	generalisation to multiple activities per cluster :

	$P(n_{gc} = a(c - c_e - 1) + \gamma + x) = {a c_e \choose x} d^x (1-d)^{a ce-x}$

	$P(n_{ge} = a(c - c_e) + \gamma + x) = {a c_e - 1 \choose x} d^x (1-d)^{a c_e-1-x}$

	$P(n_{abe} = \gamma + x) = {a(c - 1) \choose x} d^x (1-d)^{a(c-1)-x}$

	$P(n_{be} = x) = P(n_{bc} = x) = {a(c - 1) \choose x} d^x (1-d)^{a(c- 1) -x}$

	\begin{align*}
	P_{retrieve} = \left [ \sum_{n = 1}^{a(c-1) + \gamma} \left [ \sum_{k = 1}^{a} { a \choose k }   P(n_{gc} = n)^k P(n_{gc} > n)^{a-k} \right ]\left [ \sum_{x=0}^{n-1} P(n_{bc} = x) \right]^{l-a} \right ]^{c - c_e} \\ \times \left [ \sum_{n = 1}^{a(c-1) +\gamma} \left[ \sum_{k = 1} { a \choose k } P(n_{ge} = n)^k P(n_{ge} > n)^{a-k} \right ] \left [ \sum_{x=0}^{n-1} P(n_{bc} = x) \right]^{l-2} \left [ \sum_{x=0}^{n-1} P(n_{abc} = x) \right] \right ]^{c_e}
	\end{align*}
